Generating Images From Captions\\ With Attention

### 2015-11-01 iclr-paper-new.tex
fixed some notation

The $\decoder$ function of \Eqref{eq:decoder} 
is defined by the LSTM network with \textit{forget} gates 
\citep{gers_forget} at a single time-step. To generate the next 
hidden state $\hdec_t$, 
the $\decoder$ takes the previous hidden state $\hdec_{t-1}$ and
the concatenation of the latent sample $z_t$ with sentence representation $s_t$ 
as the input to the LSTM network.
%combines it with the input from both the latent sample $z_t$ and 
%sentence representation $s_t$, where
%$[v_1, v_2]$ denotes the concatenation of $v_1$ and $v_2$ into the single vector.

>>>>

The $\decoder$ function of \Eqref{eq:decoder} 
is defined by the LSTM network with \textit{forget} gates 
\citep{gers_forget} at a single time-step. To generate the next 
hidden state $\hdec_t$, 
the $\decoder$ takes the previous hidden state $\hdec_{t-1}$ and
combines it with the input from both the latent sample $z_t$ and the sentence representation $s_t$.
%combines it with the input from both the latent sample $z_t$ and 
%sentence representation $s_t$, where
%$[v_1, v_2]$ denotes the concatenation of $v_1$ and $v_2$ into the single vector.
